Convergence rate of MAP estimates \\ for the exponential family

### 2021-06-18 main.tex
Minor changes to Cramer Rao and Posterior appendix

@@

A conjugate prior for the exponential family with sufficient statistic $T(X)$ and natural parameter $\natp$ is 
\begin{align}
    \pi(\natp) 
    \propto \exp(-n_0 \bregman(\natp ; \natp_0)) 
    \propto \exp(-n_0 \logpart(\natp) + \langle n_0 \mu_0 ; \natp \rangle)
\end{align}
so we see that $\pi$ is part of the exponential family, with sufficient statistic $(\natp, \logpart(\natp))$ and natural parameters $(n_0 \mu_0 , -n_0)$. When we update this prior with Bayes formula on dataset $\cD=(x_1,\dots,x_n)$, we get a posterior $\pi(\natp | \cD)$ with natural parameters $(n_0 \mu_0 + \sum_i T(x_i) , -(n_0 + n))$. This is well detailed in \citet{agarwal2010geometric}.

@@

\begin{example}
	We can also get a closed form for the posterior of a centered gaussian variance 
	\begin{align}
		\expect[\pi(\natp|\cD)]{\bregman(\natp ; \natp_*)} = \bregman(\hat \natp_n ; \natp_*) + \frac{2}{n} \frac{\mu_*}{\hat \mu_n} + \log\frac{n}{2} - \psi(1 + \frac{n}{2})
	\end{align}
	using the mean of the \href{https://en.wikipedia.org/wiki/Inverse-gamma_distribution}{inverse Gamma distribution} and the \href{https://en.wikipedia.org/wiki/Gamma_distribution#Logarithmic_expectation_and_variance}{logarithmic expectation} of a Gamma. The using results from the MLE, we get the exact formula
	\begin{align}
		\expect[\cD\sim\natp_*]{\expect[\pi(\natp|\cD)]{\bregman(\natp ; \natp_*)}}
		= \frac{2}{n} + \frac{2}{n(n-2)} + \psi(\half[n]) - \psi(1+ \half[n])
	\end{align}
	and we bound it to 
	\begin{align}
		\inv{2n} + \frac{4}{n(n-2)}
		\leq \expect[\cD\sim\natp_*]{\expect[\pi(\natp|\cD)]{\bregman(\natp ; \natp_*)}}
		\leq 
		\inv{n} + \frac{4}{n(n-2)}
	\end{align}
	which is about twice the MLE bounds~\eqref{eq:MLE_rate}, exactly like as we observed for the gaussian mean.
\end{example}

>>>>

In our case, the bias variance decomposition tells us that we are interested in the covariance between primal and dual parameters, rather than the covariance of only of these -- $\Cov(\MAPt;\MAPm)$ rather that $\Var(\MAPm)$ or $\Var(\MAPt)$.

@@

A conjugate prior for the exponential family with sufficient statistic $T(X)$ and natural parameter $\natp$ is written as
\begin{align}
    \pi(\natp) 
    \propto \exp(-n_0 \bregman(\natp ; \natp_0)) 
    \propto \exp(-n_0 \logpart(\natp) + \langle n_0 \mu_0 ; \natp \rangle) \; .
\end{align}
We see that $\pi$ is part of the exponential family, with sufficient statistic $(\natp, \logpart(\natp))$ and natural parameters $(n_0 \mu_0 , -n_0)$. When we update this prior with Bayes formula on dataset $\cD=(x_1,\dots,x_n)$, we get a posterior $\pi(\natp | \cD)$ with natural parameters $(n_0 \mu_0 + \sum_i T(x_i) , -(n_0 + n))$. This is well detailed in \citet{agarwal2010geometric}.

@@

\begin{example}
	We can also get a closed form for the posterior of a centered gaussian variance 
	\begin{align}
		\expect[\pi(\natp|\cD)]{\bregman(\natp ; \natp_*)} = \bregman(\hat \natp_n ; \natp_*) + \frac{2}{n} \frac{\mu_*}{\hat \mu_n} + \log\frac{n}{2} - \psi(1 + \frac{n}{2})
	\end{align}
	using the mean of the \href{https://en.wikipedia.org/wiki/Inverse-gamma_distribution}{inverse Gamma distribution} and the \href{https://en.wikipedia.org/wiki/Gamma_distribution#Logarithmic_expectation_and_variance}{logarithmic expectation} of a Gamma. 
	Then using results from the MLE, we get the exact formula
	\begin{align}
		\expect[\cD\sim\natp_*]{\expect[\pi(\natp|\cD)]{\bregman(\natp ; \natp_*)}}
		= \frac{2}{n} + \frac{2}{n(n-2)} + \psi(\half[n]) - \psi(1+ \half[n])
	\end{align}
	and we bound it to 
	\begin{align}
		\inv{2n} + \frac{4}{n(n-2)}
		\leq \expect[\cD\sim\natp_*]{\expect[\pi(\natp|\cD)]{\bregman(\natp ; \natp_*)}}
		\leq 
		\inv{n} + \frac{4}{n(n-2)}
	\end{align}
	which is about twice the MLE bounds~\eqref{eq:MLE_rate}, exactly as we reportred for the gaussian mean.
\end{example}
